Where Do Population III Stars Form?

### 2019-03-29 paper.tex
Adding summary of my thoughts on simulation comparison

\noindent\textbf{JHW summary:} In all of these papers, we shouldn't be focusing on the redshift dependence because that is model dependent.  We should focus on the relationship between the LW background intensity and the halo masses.  This is the best practice because our cosmological volume is small and cannot capture the cosmic variance.  The Tegmark+ result is the absolute lowest halo mass for H2 cooling.  Trenti+ uses a similar argument as them to calculate the minimum mass that is dependent on the LW background that they calculate from their semi-analytic model.  In this discussion, I wouldn't put emphasis (e.g. in comparison with Mebane+) on our Pop III SFRD decreasing at a particular redshift because it's a small box.  In other studies (like the Renaissance and Wise12+), the Pop III SFRD is pretty flat until some later time.  None of these semi-analytic models include self-shielding.  I think it would be worthwhile to make a plot of (minimum) host halo mass and J_LW, comparining our work with others.

@@

>>>>

\noindent\textbf{JHW summary:} In all of these papers, we shouldn't be focusing on the redshift dependence because that relies on the galaxy/star formation model that has large uncertainties.  We should focus on the relationship between the LW background intensity and the halo masses.  This is the best thing to do because our cosmological volume is small and cannot capture the cosmic variance.  The Tegmark+ result is the absolute lowest halo mass for H2 cooling.  Trenti+ uses a similar argument as them to calculate the minimum mass that is dependent on the LW background that they calculate from their semi-analytic model.  In this discussion, I wouldn't put emphasis (e.g. in comparison with Mebane+) on our Pop III SFRD decreasing at a particular redshift because it's a small box.  In other studies (like the Renaissance and Wise12+), the Pop III SFRD is pretty flat until some later time.  None of these semi-analytic models include self-shielding.  I think it would be worthwhile to make a plot of (minimum) host halo mass and J\_LW, comparining our work with others.

@@

\noindent\textbf{JHW summary:} Mention that the Trenti+ and Mebane+ results have higher halo masses than the Machacek+ paper, but this is more in-line with the masses found in simulations (e.g. Wise+ \& O'Shea).  We should focus our comparison with Yoshida+ because it includes self-shielding and includes many different halos, whereas Wise+ and O'Shea+ only look at one halo.  Also, we need to figure out why the Muratov+ results have much higher halo masses even though they include self-shielding.  Is it a resolution issue or something else?
